---
title: "outliers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Remove outliers from the data (do with and without)

1. Define Quartiles and IQR for the different continuous variables

```{r cars}
# triplength_avg

Q <- quantile(HH_dt_2$triplength_avg, probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(HH_dt_2$triplength_avg)
lower_bound <- Q[1]-2.2*iqr # -18
upper_bound <- Q[2]+2.2*iqr # 34
lower_bound
upper_bound


# nummots
Q2<- quantile(HH_dt_2$nummots, probs=c(.25, .75), na.rm = FALSE)
iqr2 <- IQR(HH_dt_2$nummots)
lower_bound2 <- Q2[1]-2.2*iqr2  #0
upper_bound2 <- Q2[2]+2.2*iqr2 #3
lower_bound2
upper_bound2


#numlic
Q3 <- quantile(HH_dt_2$numlic, probs=c(.25, .75), na.rm = FALSE)
iqr3 <- IQR(HH_dt_2$numlic)
lower_bound_3 <- Q3[1]-2.2*iqr3 # -1.2
upper_bound_3 <- Q3[2]+2.2*iqr3 # 6
lower_bound_3
upper_bound_3


#numpeds
Q5<- quantile(HH_dt_2$numped, probs=c(.25, .75), na.rm = FALSE)
iqr5 <- IQR(HH_dt_2$numped)
lower_bound5 <- Q5[1]-2.2*iqr5  #-4
upper_bound5 <- Q5[2]+2.2*iqr5  #8
lower_bound5 
upper_bound5 


# workers:
Q6 <- quantile(HH_dt_2$workers, probs=c(.25, .75), na.rm = FALSE)
iqr6 <- IQR(HH_dt_2$workers)
lower_bound_6 <- Q6[1]-2.2*iqr6  #-3
upper_bound_6 <- Q6[2]+2.2*iqr6  #5
lower_bound_6 
upper_bound_6


# average number of trips

Q_trips <- quantile(HH_dt_2$tripsavg, probs=c(.25, .75), na.rm = FALSE)
iqrtrips <- IQR(HH_dt_2$tripsavg)
lower_boundtrips <- Q_trips[1]-2.2*iqrtrips # -10
upper_boundtrips <- Q_trips[2]+2.2*iqrtrips # 23
lower_boundtrips
upper_boundtrips


# income numerical 
Q_inc<- quantile(HH_dt_2$income_numerical, probs=c(.25, .75), na.rm = FALSE)
iqr_inc <- IQR(HH_dt_2$income_numerical)
lower_bound_inc <- Q_inc[1]-2.2*iqr_inc #-3
upper_bound_inc <- Q_inc[2]+2.2*iqr_inc #11.84
lower_bound_inc
upper_bound_inc


#anzkind18
Q_kind<- quantile(HH_dt_2$numch18, probs=c(.25, .75), na.rm = FALSE)
iqr_kind <- IQR(HH_dt_2$numch18)
lower_bound_kind <- Q_kind[1]-2.2*iqr_kind #0
upper_bound_kind <- Q_kind[2]+2.2*iqr_kind #2
lower_bound_kind
upper_bound_kind

```

remove outliers according to outlier labeling rule or to the rule of at least 10 observations per category
```{r}
library(dplyr)
HH_dt_2_out <- HH_dt_2
#dplyr::count(HH_dt_2, triplength_avg) # ok
HH_dt_2_out <- filter(HH_dt_2_out,triplength_avg < upper_bound)

# 3 und 4 haben relative wenige bei 0
dplyr::count(HH_dt_2, nummots, by=numcars) 
HH_dt_2_out <- filter(HH_dt_2_out,nummots < 5)

dplyr::count(HH_dt_2_out, numcars , by=region2) #ok
dplyr::count(HH_dt_2_out, region2) #ok
HH_dt_2_out <- filter(HH_dt_2_out,numlic < 5)

#dplyr::count(HH_dt_2_out, numped, by = numcars) # ok
HH_dt_2_out <- filter(HH_dt_2_out,numped < 11)

# no zero car observations for 4 workers
dplyr::count(HH_dt_2, workersall, by = numcars)
HH_dt_2_out <- filter(HH_dt_2_out,workersall < 4)


#dplyr::count(HH_dt_2_out, parttime, by = numcars)
HH_dt_2_out <- filter(HH_dt_2_out,parttime < 4) #eigentlich kleiner 3

HH_dt_2_out <- dplyr::filter(HH_dt_2_out,tripsavg < upper_boundtrips)

#dplyr::count(HH_dt_2, income_numerical < 0.5)#ok
HH_dt_2_out <- dplyr::filter(HH_dt_2_out,income_numerical < upper_bound_inc)
HH_dt_2_out <- dplyr::filter(HH_dt_2_out,income_numerical > lower_bound_inc)

# 8 instead of 10 observations for four children and zero cars
#dplyr::count(HH_dt_2, numch18, by = numcars) #ok
#HH_dt_2_out <- filter(HH_dt_2_out, numch18 < 5)

#dplyr::count(HH_dt_2, num2039,  by=numcars)
#dplyr::count(HH_dt_2, num4064, by=numcars)

#dplyr::count(HH_dt_2_out, numlic, by=numcars)
#dplyr::count(HH_dt_2, oldHH, by=numcars)

#HH_dt_2_out <- filter(HH_dt_2_out, num2039 < 5)
#HH_dt_2_out <- filter(HH_dt_2_out, num4064 < 4)
#HH_dt_2_out <- filter(HH_dt_2_out, anzahlold < 4)


#categorical variables: 

#dplyr::count(HH_dt_2, CS,  by=numcars)#ok
#dplyr::count(HH_dt_2, bus28,  by=numcars)#ok
#dplyr::count(HH_dt_2, metro28,  by=numcars)#ok
#dplyr::count(HH_dt_2, train28,  by=numcars)#OK
#dplyr::count(HH_dt_2, hh_children,  by=numcars) #ok
#dplyr::count(HH_dt_2, education,  by=numcars) #ok
#dplyr::count(HH_dt_2, quali_nv,  by=numcars) #ok
#dplyr::count(HH_dt_2, quali_opnv,  by=numcars) #ok
#dplyr::count(HH_dt_2_out,housing_type,  by=numcars) #ok
#dplyr::count(HH_dt_2, garage,  by=numcars) # ok

#dt_other <- filter(HH_dt_2_out, housing_type == "other")
```

Testing correlation 

1. Numerical/Ordinal by Numerical/ordinal correlation incl. plot

```{r}

# Source: http://www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-using-r-software


# correlation between all numerical and ordinal variables
# spearman correlation coefficient

corr_dt <- HH_dt_2_out[, c("tripsavg", "numlic", "workers", "parttime", "triplength_avg","hhsize", "nummots", "numped", "income_numerical", "bus28", "metro28", "train28","quali_opnv", "quali_nv")]

# transform factors to ranks
corr_dt$bus28 <- as.numeric(corr_dt$bus28)
corr_dt$train28 <- as.numeric(corr_dt$train28)
corr_dt$metro28 <- as.numeric(corr_dt$metro28)
corr_dt$quali_nv <- as.numeric(corr_dt$quali_nv)
corr_dt$quali_opnv <- as.numeric(corr_dt$quali_opnv)

colnames(corr_dt) <-  c("av.trips", "licenses", "fulltime", "parttime", "av.triplength","hhsize", "motorbikes", "bikes", "income", "bus", "metro", "train","quality_ps", "quality_pt")



# show correlation-plot
corr2 <- rcorr(as.matrix(corr_dt), type="spearman")

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

flattenCorrMatrix(corr2$r, corr2$P)
corrplot(corr2$r, type="upper", order="hclust", sig.level = 0.01, insig = "blank")

corr2_dt <- as.data.frame(flattenCorrMatrix(corr2$r, corr2$P))
highvalues_dt <- filter(corr2_dt, cor > 0.5 | cor < -0.5)



# remove hhsize due to correlation
HH_dt_2[, hhsize := NULL]

```

Categorical/ordinal by categorical/ordinal correlation 

```{r}
#Kategorische Variablen 
#Using Cramer's V if one variable is more than 2, if both are dichotomous: cramers phi
#can be used for nominal and ordinal variables

#Packages for Cramers V 
#install.packages("vcd")
library(vcd)

#Codesource: https://stackoverflow.com/questions/22515525/is-it-possible-to-speed-up-my-function-for-creating-a-correlation-matrix

# import all categorical and ordinal columns

corrcat_dt <- HH_dt_2[, c("CS","income_gr", "bus28", "train28", "metro28", "housing_type", "garage", "quali_opnv", "quali_nv","single", "couple", "couple_children", "single_parent", "other_ind", "region1", "region2", "education", "trips", "numlic", "numch18", "workers" , "num2039", "num4064", "nummots", "numped", "householdtype_all")]
corrcat_dt <- as.data.frame(corrcat_dt)

# convert into factor columns
for(i in 1:ncol(corrcat_dt)){

corrcat_dt[,i] <- as.factor(corrcat_dt[,i])

}

#calculate Cramers_V for all pairs of categorical variables in the table:
cv <- function(x, y) {
  t <- table(x, y)
  print(t)
  chi <- suppressWarnings(chisq.test(t))$statistic
  cramer <- sqrt(chi / (NROW(x) * (min(dim(t)) - 1)))
  cramer
}

get.V3<-function(y, fill = TRUE){
  col.y<-ncol(y)
  V<-matrix(ncol=col.y,nrow=col.y)
  for(i in 1:(col.y - 1)){
    print(i)
    for(j in (i + 1):col.y){
      print(j)
      V[i,j]<-cv(y[,i],y[,j])
    }
  }
  diag(V) <- 1 
  if (fill) {
    for (i in 1:ncol(V)) {
      V[, i] <- V[i, ]
    }
  }
  V
}


cramer_table <- get.V3(corrcat_dt)

colnames(cramer_table) <- colnames(corrcat_dt)
rownames(cramer_table) <- colnames(corrcat_dt)

# add degress of freedom
levels <- c(1:ncol(corrcat_dt))
for(i in 1:ncol(corrcat_dt)){

levels[i] <- nlevels(corrcat_dt[,i])

}

cramer_table$df <- levels
cramer_table <- rbind(round(levels,0),cramer_table)

# check thresholds:
#http://www.real-statistics.com/chi-square-and-f-distributions/effect-size-chi-square/

cramer_table
```

Numerical vs. categorical 

```{r}
#look at correlation between predicted numerical values for triplength_avg and actual values by a linear model using the categorical variable as a predictor

#https://stats.stackexchange.com/questions/119835/correlation-between-a-nominal-iv-and-a-continuous-dv-variable/124618#124618


# all really small, no correlation

model.lm <- lm(triplength_avg ~ CS, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ householdtype_all, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ education, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ region1, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ region2, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ housing_type, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

model.lm <- lm(triplength_avg ~ garage, data = HH_dt_2)
summary(model.lm)
rsq <- summary(model.lm)$r.squared
sqrt(rsq)

```

VIF

```{r}
#VIF
#The VIF may be calculated for each predictor by doing a linear regression of that predictor on all the other predictors, and then obtaining the R2 from that regression. The VIF is just 1/(1-R2).
# for dummies square gvif^(1/2...) and apply same rule as to VIF


HH_dt_2_out$numcars <- as.numeric(as.character(HH_dt_2_out$numcars))
x_reg <- lm(numcars ~  numlic + region2 + income_numerical + quali_nv + workers + parttime +  hh_children +CSyes + CSmultiple + triplength_avg + nummots + numped + oldHH + education + housing_type + quali_opnv + train28 + bus28 + metro28 + garage + tripsavg + education, data = HH_dt_2_out)
x <- vif(x_reg)

x

x <- as.data.frame(x)
x <- rownames_to_column(x)

x$rowname[x$rowname=="numlic"] <- "Number of Licenses"
x$rowname[x$rowname=="income_numerical"] <- "Income"
x$rowname[x$rowname=="triplength_avg"] <- "Average triplength"
x$rowname[x$rowname=="workers"] <- "Number of workers"
x$rowname[x$rowname=="metro28"] <- "Distance to next metrostation"
x$rowname[x$rowname=="numped"] <- "Number of bikes/pedelecs"
x$rowname[x$rowname=="tripsavg"] <- "Average number of trips"
x$rowname[x$rowname=="CSyes"] <- "Carsharing available"
x$rowname[x$rowname=="oldHH"] <- "Old household"
x$rowname[x$rowname=="education"] <- "Highest educational degree"
x$rowname[x$rowname=="housing_type"] <- "Type of housing"
x$rowname[x$rowname=="quali_opnv"] <- "Quality of public transport"
x$rowname[x$rowname=="train28"] <- "Distance to nearest trainstation"
x$rowname[x$rowname=="bus28"] <- "Distance to nearest bus stop"
x$rowname[x$rowname=="housing_type"] <- "Type of housing"

```


Overview table

```{r}
library(data.table)
relevant_vars <- names(fit_new$model)[2:21]
relevant_vars2 <- relevant_vars
relevant_vars2[8] <- "nummots"
Overview_df <- HH_dt_2_out[,relevant_vars2, with=FALSE] 
alloc.col(Overview_df, 200)
Overview_dummies <- fastDummies::dummy_cols(Overview_df, remove_selected_columns = TRUE)

variables_Overview <- apply(Overview_dummies,2,mean)
variables_Overview <- as.data.frame(variables_Overview)
variables_Overview <- rownames_to_column(variables_Overview)

variables_Overview$rowname[variables_Overview$rowname=="numlic"] <- "Number of Licenses"
variables_Overview$rowname[variables_Overview$rowname=="income_numerical"] <- "Monthly household income in thousand Euro"
variables_Overview$rowname[variables_Overview$rowname=="triplength_avg"] <- "Average triplength in kilometers"
variables_Overview$rowname[variables_Overview$rowname=="workers"] <- "Number of full-time workers"
variables_Overview$rowname[variables_Overview$rowname=="numped"] <- "Number of bikes / pedelecs"
variables_Overview$rowname[variables_Overview$rowname=="tripsavg"] <- "Average number of daily trips"
variables_Overview$rowname[variables_Overview$rowname=="CSyes_1"] <- "1 if carsharing available"
variables_Overview$rowname[variables_Overview$rowname=="CSmultiple_1"] <- "1 if multiple carsharing options available"
variables_Overview$rowname[variables_Overview$rowname=="nummots"] <- "Number of motorbikes / mopeds"
variables_Overview$rowname[variables_Overview$rowname=="parttime"] <- "Number of part-time workers"
variables_Overview$rowname[variables_Overview$rowname=="region2_suburban"] <- "1 if households lives in an suburban environment"
variables_Overview$rowname[variables_Overview$rowname=="region2_rural"] <- "1 if households lives in an rural environment"
variables_Overview$rowname[variables_Overview$rowname=="oldHH_1"] <- "1 if categorized as old household"
variables_Overview$rowname[variables_Overview$rowname=="hh_children_1"] <- "1 if household has children"
variables_Overview$rowname[variables_Overview$rowname=="housing_type_multifamily_h"] <- "1 if residence is a multifamily-Home"
variables_Overview$rowname[variables_Overview$rowname=="housing_type_apartmentbuilding"] <- "1 if residence is an apartmentbuilding"
variables_Overview$rowname[variables_Overview$rowname=="housing_type_singlefamily_h"] <- "1 if residence is a singlefamily-Home (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="housing_type_other"] <- "1 if residence is another housing type"
variables_Overview$rowname[variables_Overview$rowname=="region2_urban"] <- "1 if households lives in an urban environment (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="garage_1"] <- "1 if a garage is available"

variables_Overview$rowname[variables_Overview$rowname=="quali_nv_1"] <- "Quality of public services: 1 (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="quali_nv_2"] <- "Quality of public services: 2"

variables_Overview$rowname[variables_Overview$rowname=="quali_nv_3"] <- "Quality of public services: 3"

variables_Overview$rowname[variables_Overview$rowname=="quali_nv_4"] <- "Quality of public services: 4"

variables_Overview$rowname[variables_Overview$rowname=="quali_opnv_1"] <- "Quality of public transport: 1 (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="quali_opnv_2"] <- "Quality of public transport: 2"
variables_Overview$rowname[variables_Overview$rowname=="quali_opnv_3"] <- "Quality of public transport: 3"
variables_Overview$rowname[variables_Overview$rowname=="quali_opnv_4"] <- "Quality of public transport: 4"

variables_Overview$rowname[variables_Overview$rowname=="bus28_near"] <- "Nearest bus stop: air-line distance below 500m (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="bus28_middle"] <- "Nearest bus stop: air-line distance between 500m to 2500m"
variables_Overview$rowname[variables_Overview$rowname=="bus28_far"] <- "Nearest bus stop: air-line distance between 2500 to 5000m"
variables_Overview$rowname[variables_Overview$rowname=="bus28_rfar"] <- "Nearest bus stop: air-line distance above 5000m"

variables_Overview$rowname[variables_Overview$rowname=="train28_near"] <- "Nearest train station: air-line distance below 500m (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="train28_middle"] <- "Nearest train station: air-line distance between 500m to 2500m"
variables_Overview$rowname[variables_Overview$rowname=="train28_far"] <- "Nearest train station: air-line distance between 2500 to 5000m"
variables_Overview$rowname[variables_Overview$rowname=="train28_rfar"] <- "Nearest train station: air-line distance above 5000m"

variables_Overview$rowname[variables_Overview$rowname=="metro28_near"] <- "Nearest metro/tram station: air-line distance below 500m (basecategory)"
variables_Overview$rowname[variables_Overview$rowname=="metro28_middle"] <- "Nearest metro/tram station: air-line distance between 500m to 2500m"
variables_Overview$rowname[variables_Overview$rowname=="metro28_far"] <- "Nearest metro/tram station: air-line distance between 2500 to 5000m"
variables_Overview$rowname[variables_Overview$rowname=="metro28_rfar"] <- "Nearest metro/tram station: air-line distance above 5000m"

variables_Overview <- rbind(variables_Overview, data.frame(rowname = "1 if Carsharing not available (Basecategory)", variables_Overview = 1 - (variables_Overview$variables_Overview[variables_Overview$rowname=="1 if carsharing available"]) - (variables_Overview$variables_Overview[variables_Overview$rowname=="1 if multiple carsharing options available"])))

variables_Overview <- variables_Overview[!(variables_Overview$rowname %in% c("CSyes_0","CSmultiple_0","oldHH_0", "hh_children_0", "garage_0")), ]

overview_names <- 1:41
variables_Overview2 <- cbind(overview_names, variables_Overview)

#maketable in latex

library(xtable)
#install.packages("xtable")
print(xtable(variables_Overview2, type = "latex", digits=c(0,0,0,3)), include.rownames=FALSE, file = "overview.tex")



```


Preliminary model
```{r}
fit_multinom_null <- multinom(numcars ~ 1, data = HH_dt_2_out,maxit=300)

result_stepAIC1 <- stepAIC(fit_multinom_null, direction="forward", scope = list(upper = ~ numlic + region2 + income_numerical+ quali_nv + CSyes + CSmultiple + workers  + triplength_avg+ nummots+ housing_type + quali_opnv + oldHH + hh_children + garage + metro28 + train28 + tripsavg + parttime + numped + bus28))

result_stepAIC1

fit_preliminary <- multinom(numcars ~ numlic + region2 + income_numerical + 
    quali_nv + CSyes + workers + CSmultiple + nummots + housing_type + 
    triplength_avg + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28, data = HH_dt_2_out,maxit=300)

coef_prel <- coef(fit_preliminary)
coef_prel <- as.data.frame(coef_prel)

texreg::extract(fit_preliminary)
texreg::texreg(fit_preliminary)
```


Make binary models for further analysis

Testing linearity assumption between dependent variable and continuous independent variables
http://www.statisticalassociates.com/logistic10.htm
The right-hand predictor side of the equation must be linear with the left-hand outcome side of the equation. You must test for linearity in the logit (in logistic regression the logit is the outcome side). 
Done via separate logistic regression between 0 and 1 cars, 0 and 2 cars, 0 and 3 cars


```{r}



HH_dt_bin1  <- filter(HH_dt_2_out, (numcars == 0 | numcars ==1))
HH_dt_bin2 <- filter(HH_dt_2_out, (numcars == 0 | numcars ==2))
HH_dt_bin3 <- filter(HH_dt_2_out, (numcars == 0 | numcars ==3))
#dplyr::count(HH_dt_bin1, numcars)
#dplyr::count(HH_dt_bin2, numcars)
#dplyr::count(HH_dt_bin3, numcars)

HH_dt_bin2$numcars <- as.numeric(as.character(HH_dt_bin2$numcars))
HH_dt_bin2$numcars <- HH_dt_bin2$numcars/2

HH_dt_bin3$numcars <- as.numeric(as.character(HH_dt_bin3$numcars))
HH_dt_bin3$numcars <- HH_dt_bin3$numcars/3


mylogit <- glm(numcars  ~ numlic + region2 + income_numerical + 
    quali_nv + CSyes + workers + CSmultiple + nummots + housing_type + 
    triplength_avg + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28, data = HH_dt_bin1, family = "binomial")

coeflog1 <- coef(mylogit)
coeflog1 <- as.data.frame(coeflog1)


mylogit2 <- glm(numcars  ~ numlic + region2 + income_numerical + 
    quali_nv + CSyes + workers + CSmultiple + nummots + housing_type + 
    triplength_avg + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28, data = HH_dt_bin2, family = "binomial")

coeflog2 <- coef(mylogit2)
coeflog2 <- as.data.frame(coeflog2)


mylogit3 <- glm(numcars  ~ numlic + region2 + income_numerical + 
    quali_nv + CSyes + workers + CSmultiple + nummots + housing_type + 
    triplength_avg + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28, data = HH_dt_bin3, family = "binomial")


coeflog3 <- coef(mylogit3)
coeflog3 <- as.data.frame(coeflog3)


```


Table comparing separate logits and preliminary model 

```{r}
#transpose coef_prel 
coef_prel_t <- as.data.frame(t(as.matrix(coef_prel)))

coeflog1$prel <- coef_prel_t$`1`
coeflog2$prel <- coef_prel_t$`2`
coeflog3$prel <- coef_prel_t$`3`

coefs_total<-cbind(coeflog1, coeflog2, coeflog3)
coefs_total <- rownames_to_column(coefs_total)

coefs_total$rowname[coefs_total$rowname=="numlic"] <- "licenses"
coefs_total$rowname[coefs_total$rowname=="income_numerical"] <- "income"
coefs_total$rowname[coefs_total$rowname=="triplength_avg"] <- "av.triplength"
coefs_total$rowname[coefs_total$rowname=="workers"] <- "fulltime"
coefs_total$rowname[coefs_total$rowname=="numped"] <- "bikes"
coefs_total$rowname[coefs_total$rowname=="tripsavg"] <- "av.trips"
coefs_total$rowname[coefs_total$rowname=="CSyes1"] <- "carsharing"
coefs_total$rowname[coefs_total$rowname=="CSmultiple1"] <- "m.carsharing"
coefs_total$rowname[coefs_total$rowname=="nummots"] <- "motorbikes"
coefs_total$rowname[coefs_total$rowname=="parttime"] <- "parttime"
coefs_total$rowname[coefs_total$rowname=="region2suburban"] <- "suburban"
coefs_total$rowname[coefs_total$rowname=="region2rural"] <- "rural"
coefs_total$rowname[coefs_total$rowname=="oldHH1"] <- "old"
coefs_total$rowname[coefs_total$rowname=="hh_children1"] <- "children"
coefs_total$rowname[coefs_total$rowname=="housing_typemultifamily_h"] <- "multifamily"
coefs_total$rowname[coefs_total$rowname=="housing_typeapartmentbuilding"] <- "apartmentbuilding"
coefs_total$rowname[coefs_total$rowname=="housing_typeother"] <- "other"
coefs_total$rowname[coefs_total$rowname=="garage1"] <- "garage"

coefs_total$rowname[coefs_total$rowname=="quali_nv2"] <- "ps.2"
coefs_total$rowname[coefs_total$rowname=="quali_nv3"] <- "ps.3"
coefs_total$rowname[coefs_total$rowname=="quali_nv4"] <- "ps.4"


coefs_total$rowname[coefs_total$rowname=="quali_opnv2"] <- "pt.2"
coefs_total$rowname[coefs_total$rowname=="quali_opnv3"] <- "pt.3"
coefs_total$rowname[coefs_total$rowname=="quali_opnv4"] <- "pt.4"


coefs_total$rowname[coefs_total$rowname=="bus28_middle"] <- "bus.2"
coefs_total$rowname[coefs_total$rowname=="bus28_far"] <- "bus.3"
coefs_total$rowname[coefs_total$rowname=="bus28_rfar"] <- "bus.4"


coefs_total$rowname[coefs_total$rowname=="train28_middle"] <- "train.2"
coefs_total$rowname[coefs_total$rowname=="train28_far"] <- "train.3"
coefs_total$rowname[coefs_total$rowname=="train28_rfar"] <- "train.4"

coefs_total$rowname[coefs_total$rowname=="metro28_middle"] <- "metro.2"
coefs_total$rowname[coefs_total$rowname=="metro28_far"] <- "metro.3"
coefs_total$rowname[coefs_total$rowname=="metro28_rfar"] <- "metro.4"

print(xtable(coefs_total, type = "latex",digits=c(0,0,3,3,3,3,3,3)),include.rownames=FALSE, file = "tableseparatelogits.tex")


```


Plot continuous variables against the logit
```{r}


#http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

#logit1
probabilities <- predict(mylogit, type = "response")
mydata <- HH_dt_bin1[,c('numlic', 'workers', 'parttime', 'nummots', 'triplength_avg', 'income_numerical', 'tripsavg', 'numped')]
predictors <- colnames(mydata)

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess" ,span = 0.01, size = 1) + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y", labeller = labeller(predictors = 
    c("income_numerical" = "income",
      "nummots" = "motorbikes",
      "numlic" = "licenses",
      "workers" = "fulltime",
      "parttime" = "parttime",
      "triplength_avg" = "av.triplength",
      "tripsavg" = "av.trips",
      "numped" = "bikes")))

```

```{r}
# logit2
probabilities <- predict(mylogit2, type = "response")
mydata <- HH_dt_bin2[,c('numlic', 'workers', 'parttime1', 'nummots', 'triplength_avg', 'income_numerical', 'tripsavg', 'numped')]
predictors <- colnames(mydata)

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess",span = 0.01, size = 1) + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y",labeller = labeller(predictors = 
    c("income_numerical" = "income",
      "nummots" = "motorbikes",
      "numlic" = "licenses",
      "workers" = "fulltime",
      "parttime1" = "parttime",
      "triplength_avg" = "av.triplength",
      "tripsavg" = "av.trips",
      "numped" = "bikes")))
```



```{r}

# logit 3
probabilities <- predict(mylogit3, type = "response")
mydata <- HH_dt_bin3[,c('numlic', 'workers', 'parttime', 'nummots', 'triplength_avg', 'income_numerical', 'tripsavg', 'numped')]
predictors <- colnames(mydata)

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess",span = 0.01, size = 1) + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y", labeller = labeller(predictors = 
    c("income_numerical" = "income",
      "nummots" = "motorbikes",
      "numlic" = "licenses",
      "workers" = "fulltime",
      "parttime" = "parttime",
      "triplength_avg" = "av.triplength",
      "tripsavg" = "av.trips",
      "numped" = "bikes")))
```


Making binned plots and look at residuals

Binned plots logit 1 (look at them before and after inserting transformations)
```{r}

x <- predict(mylogit, type="response")
y <- resid(mylogit, type= "response")

#library(arm)
binnedplot(HH_dt_bin1$triplength_avg,y, main="Binned plot: Av.triplength",ylab="Logit1: Average residual") #ok
binnedplot(HH_dt_bin1$income_numerical,y, main="Binned plot: Income",ylab="Logit1: Average residual")#ok
binnedplot(HH_dt_bin1$numlic,y, main="Binned plot: Licenses",ylab="Logit1: Average residual")#ok
binnedplot(HH_dt_bin1$tripsavg,y, main="Binned plot: Av.trips",ylab="Logit1: Average residual")#ok
binnedplot(HH_dt_bin1$workers,y, main="Binned plot: Fulltime",ylab="Logit1: Average residual")#ok
binnedplot(HH_dt_bin1$parttime,y, main="Binned plot: Parttime",ylab="Logit1: Average residual")#ok
binnedplot(HH_dt_bin1$nummots,y, main="Binned plot: Motorbikes",ylab="Logit1: Average residual") #ok
binnedplot(HH_dt_bin1$numped,y, main="Binned plot: Bikes",ylab="Logit1: Average residual") # ok
binnedplot(x,y, main="Binned plot: Overall",ylab="Logit1: Average residual")

HH_dt_bin1$nummots1 = HH_dt_bin1$nummots
HH_dt_bin1$nummots1[HH_dt_bin1$nummots == 0] <- HH_dt_bin1$nummots1[HH_dt_bin1$nummots == 0] + 0.0001


mylogit <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime + I(parttime^2) + tripsavg +  
    hh_children + numped + metro28 + train28 + garage + bus28, data = HH_dt_bin1, family = "binomial")

library(broom)
library(dplyr)
datalogit1 <- augment(mylogit) %>% 
  dplyr::mutate(index = 1:n()) 
datalogit1$HHID <- HH_dt_bin1$HH_ID
influentials1 <- datalogit1 %>% 
  filter(abs(.std.resid) > 3)


datalogit2 <- augment(mylogit2) %>% 
  dplyr::mutate(index = 1:n()) 
datalogit2$HHID <- HH_dt_bin2$HH_ID
influentials2 <- datalogit2 %>% 
  filter(abs(.std.resid) > 3)

datalogit3 <- augment(mylogit3) %>% 
  dplyr::mutate(index = 1:n()) 
datalogit3$HHID <- HH_dt_bin3$HH_ID
influentials3 <- datalogit3 %>% 
  filter(abs(.std.resid) > 3)

HHID_logit1 <- as.numeric(as.character(influentials1$HHID))
HHID_logit2 <- as.numeric(as.character(influentials2$HHID))
HHID_logit3 <- as.numeric(as.character(influentials3$HHID))


temp_influentials <- c(HHID_logit1,HHID_logit2,HHID_logit3)
HH_dt_2_out <- filter(HH_dt_2_out,!(HH_ID %in% temp_influentials))

duplicates(temp_influentials)

HH_dt_2_out$nummots1 = HH_dt_2_out$nummots
HH_dt_2_out$nummots1[HH_dt_2_out$nummots == 0] <- HH_dt_2_out$nummots1[HH_dt_2_out$nummots == 0] + 0.0001

```

Binned plots logit 2 (look at them before and after inserting transformations)

```{r}
x2 <- predict(mylogit2, type="response")
y2 <- resid(mylogit2, type= "response")

binnedplot(HH_dt_bin2$triplength_avg,y2, main="Binned plot: Av.triplength",ylab="Logit2: Average residual") #ok
binnedplot(HH_dt_bin2$income_numerical,y2, main="Binned plot: Income",ylab="Logit2: Average residual")#ok
binnedplot(HH_dt_bin2$numlic,y2, main="Binned plot: Licenses",ylab="Logit2: Average residual")#ok
binnedplot(HH_dt_bin2$tripsavg,y2, main="Binned plot: Av.trips",ylab="Logit2: Average residual")#ok
binnedplot(HH_dt_bin2$workers,y2, main="Binned plot: Fulltime",ylab="Logit2: Average residual")#ok
binnedplot(HH_dt_bin2$parttime,y2, main="Binned plot: Parttime",ylab="Logit2: Average residual")#ok
binnedplot(HH_dt_bin2$nummots,y2, main="Binned plot: Motorbikes",ylab="Logit2: Average residual") #ok
binnedplot(HH_dt_bin2$numped,y2, main="Binned plot: Bikes",ylab="Logit2: Average residual") # ok
binnedplot(x2,y2, main="Binned plot: Overall",ylab="Logit2: Average residual")

HH_dt_bin2$nummots1 = HH_dt_bin2$nummots
HH_dt_bin2$nummots1[HH_dt_bin2$nummots == 0] <- HH_dt_bin2$nummots1[HH_dt_bin2$nummots == 0] + 0.0001

mylogit2 <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime + I(parttime^2) + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28 , data = HH_dt_bin2, family = "binomial")
```

Binned plots logit 3 (look at them before and after inserting transformations)

```{r}

x3 <- predict(mylogit3, type="response")
y3 <- resid(mylogit3, type= "response")

binnedplot(HH_dt_bin3$triplength_avg,y3, main="Binned plot: Av.triplength",ylab="Logit3: Average residual") #ok
binnedplot(HH_dt_bin3$income_numerical,y3, main="Binned plot: Income",ylab="Logit3: Average residual")#ok
binnedplot(HH_dt_bin3$numlic,y3, main="Binned plot: Licenses",ylab="Logit3: Average residual")#ok
binnedplot(HH_dt_bin3$tripsavg,y3, main="Binned plot: Av.trips",ylab="Logit3: Average residual")#ok
binnedplot(HH_dt_bin3$workers,y3, main="Binned plot: Fulltime",ylab="Logit3: Average residual")#ok
binnedplot(HH_dt_bin3$parttime,y3, main="Binned plot: Parttime",ylab="Logit3: Average residual")#ok
binnedplot(HH_dt_bin3$nummots,y3, main="Binned plot: Motorbikes",ylab="Logit3: Average residual") #ok
binnedplot(HH_dt_bin3$numped,y3, main="Binned plot: Bikes",ylab="Logit3: Average residual") # ok
binnedplot(x3,y3, main="Binned plot: Overall",ylab="Logit3: Average residual")

HH_dt_bin3$nummots1 = HH_dt_bin3$nummots
HH_dt_bin3$nummots1[HH_dt_bin3$nummots == 0] <- HH_dt_bin3$nummots1[HH_dt_bin3$nummots == 0] + 0.0001


mylogit3 <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime +I(parttime^2) +tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28 , data = HH_dt_bin3, family = "binomial")

```


Change logits according to nonlinear associatons: logit1 
```{r}
# only add a small constant to 0 values of a column 

HH_dt_bin1$nummots1 = HH_dt_bin1$nummots
HH_dt_bin1$nummots1[HH_dt_bin1$nummots == 0] <- HH_dt_bin1$nummots1[HH_dt_bin1$nummots == 0] + 0.0001

HH_dt_bin1$parttime1 = HH_dt_bin1$parttime
HH_dt_bin1$parttime1[HH_dt_bin1$parttime == 0] <- HH_dt_bin1$parttime1[HH_dt_bin1$parttime == 0] + 0.0001

#HH_dt_bin1$shareworkers <- HH_dt_bin1$workers / HH_dt_bin1$hhsize

#HH_dt_bin1$sharedrivers1 = HH_dt_bin1$sharedrivers
#HH_dt_bin1$sharedrivers1[HH_dt_bin1$sharedrivers == 0] <- HH_dt_bin1$sharedrivers1[HH_dt_bin1$sharedrivers == 0] + 0.0001

mylogit <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + I(numped^2) + metro28 + train28 + garage + bus28 , data = HH_dt_bin1, family = "binomial")

#mylogit <- glm(numcars ~ numlic + region2 + income_numerical + 
    #I(numlic^2) + quali_nv + I(income_numerical^2) + CSyes + 
    #workersall + CSmultiple + log(nummots1) + triplength_avg + housing_type+
    #quali_opnv + I(triplength_avg^2) + oldHH + hh_children + numped + tripsavg + metro28 + train28 + garage + 
    #bus28, data = HH_dt_bin1, family = "binomial")


#plot(mylogit)


#19833
#37738 / 14924
#19137

model.data1 <- augment(mylogit) %>% 
dplyr::mutate(index = 1:n()) 
model.data1 %>% top_n(3, .cooksd)
model.data1$HHID <- HH_dt_bin1$HH_ID
influentials1 = model.data1 %>% 
filter(abs(.std.resid) > 3)
influentials1


templogit1 <- c(14925,14947, 37742)
HHID_logit1 <- influentials1$HHID[influentials1$index %in% templogit1]

HH_dt_bin1 <- filter(HH_dt_bin1, !(HH_ID %in% HHID_logit1))
#HH_dt_bin1 <- filter(HH_dt_bin1, !(HH_ID %in% influentials1$HHID))

mylogit <- glm(numcars ~  numlic + I(numlic^2) + region2 + income_numerical+quali_nv + CSyes + CSmultiple + workers + I(workers^2) + triplength_avg+ I(triplength_avg^2) + log(nummots1)+ housing_type + quali_opnv + oldHH+ hh_children + garage + metro28 + train28 + tripsavg + parttime + numped + I(numped^2)+ bus28, data = HH_dt_bin1,family = "binomial")



```


Change logits according to nonlinear associatons: logit2

```{r}


HH_dt_bin2$nummots1 = HH_dt_bin2$nummots
HH_dt_bin2$nummots1[HH_dt_bin2$nummots == 0] <- HH_dt_bin2$nummots1[HH_dt_bin2$nummots == 0] + 0.0001

HH_dt_bin2$parttime1 = HH_dt_bin2$parttime
HH_dt_bin2$parttime1[HH_dt_bin2$parttime == 0] <- HH_dt_bin2$parttime1[HH_dt_bin2$parttime == 0] + 0.0001

#HH_dt_bin2$sharedrivers1 = HH_dt_bin2$sharedrivers
#HH_dt_bin2$sharedrivers1[HH_dt_bin2$sharedrivers == 0] <- HH_dt_bin2$sharedrivers1[HH_dt_bin2$sharedrivers == 0] + 0.0001

mylogit2 <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + I(numped^2) + metro28 + train28 + garage + bus28 , data = HH_dt_bin2, family = "binomial")


#mylogit2 <- glm(numcars ~ numlic + region2 + income_numerical +  I(numlic^2) + quali_nv + I(income_numerical^2) + CSyes +workers + CSmultiple + log(nummots1) + triplength_avg + housing_type + quali_opnv + I(triplength_avg^2) + oldHH + parttime +hh_children + numped + tripsavg + metro28 + train28 + garage + bus28, data = HH_dt_bin2, family = "binomial")

plot(mylogit2)
#15347
#20378
#7235

model.data2 <- augment(mylogit2) %>% 
dplyr::mutate(index = 1:n()) 
model.data2 %>% top_n(3, .cooksd)
model.data2$HHID <- HH_dt_bin2$HH_ID
influentials2 = model.data2 %>% 
filter(abs(.std.resid) > 3)

templogit2 <- c(15349,10847,14315)
HHID_logit2 <- influentials2$HHID[influentials2$index %in% templogit2]

HH_dt_bin2 <- filter(HH_dt_bin2, !(HH_ID %in% HHID_logit2))

mylogit2 <- glm(numcars ~   numlic + I(numlic^2) + region2 + income_numerical+ quali_nv + CSyes + CSmultiple + workers +triplength_avg+ I(triplength_avg^2) + log(nummots1)+ housing_type + quali_opnv + share2039 + shareold + hh_children + garage + metro28 + train28 + tripsavg + parttime + numped + bus28 , data = HH_dt_bin2, family = "binomial")






```


Change logits according to nonlinear associatons: logit3

```{r}

HH_dt_bin3$nummots1 = HH_dt_bin3$nummots
HH_dt_bin3$nummots1[HH_dt_bin3$nummots == 0] <- HH_dt_bin3$nummots1[HH_dt_bin3$nummots == 0] + 0.0001

#HH_dt_bin3$parttime1 = HH_dt_bin3$parttime
#HH_dt_bin3$parttime1[HH_dt_bin3$parttime == 0] <- HH_dt_bin3$parttime1[HH_dt_bin3$parttime == 0] + 0.0001


#mylogit3 <- glm(numcars ~  numlic + region2 + income_numerical +  I(numlic^2) + quali_nv + I(income_numerical^2) + CSyes +workers + CSmultiple + log(nummots1) + triplength_avg + housing_type + quali_opnv + I(triplength_avg^2) + oldHH + parttime +hh_children + numped + tripsavg + metro28 + train28 + garage + bus28, data = HH_dt_bin3, family = "binomial")

mylogit3 <- glm(numcars  ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + I(numped^2) + metro28 + train28 + garage + bus28 , data = HH_dt_bin3, family = "binomial")


#Extract model results logit3 and remove all influential points as here are less and more heterogenous observations
plot(mylogit3)
model.data <- augment(mylogit3) %>% 
dplyr::mutate(index = 1:n()) 
model.data %>% top_n(4, .cooksd)
model.data$HHID <- HH_dt_bin3$HH_ID
influentials = model.data %>% 
filter(abs(.std.resid) > 3)
influentials

HH_dt_bin3 <- filter(HH_dt_bin3, !(HH_ID %in% influentials$HHID))

templogit3 <- c(4454,8595,3569)
templogit3 <- c(11919,8517,4402)
HHID_logit3 <- influentials$HHID[influentials$index %in% templogit3]

HH_dt_bin3 <- filter(HH_dt_bin3, !(HH_ID %in% HHID_logit3))

mylogit3 <- glm(numcars ~    numlic + I(numlic^2) + region2 + income_numerical+ quali_nv + CSyes + CSmultiple + workers +triplength_avg+ I(triplength_avg^2) + log(nummots1)+ housing_type + quali_opnv + share2039 + shareold + hh_children + garage + metro28 + train28 + tripsavg + parttime + numped + bus28 , data = HH_dt_bin3, family = "binomial")

#64610800

```

Merge all higly influential points to remove them from the big dataframe

```{r}
#http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/ ( for higly influential points)


#influential_HHID <- influentials$HHID
#influential_HHID <- as.numeric(as.character(influentials$HHID))
#HHID_logit1 <- as.numeric(as.character(HHID_logit1))
#HHID_logit2 <- as.numeric(as.character(HHID_logit2))
#HHID_logit3 <- as.numeric(as.character(HHID_logit3))
#temp100 = c(influential_HHID,HHID_logit1, HHID_logit2)
temp_influentials <- c(influentials1$HHID,influentials2$HHID, influentials3$HHID)
HH_dt_2_out <- filter(HH_dt_2_out,!(HH_ID %in% temp_influentials))

HH_dt_2_out$nummots1 = HH_dt_2_out$nummots
HH_dt_2_out$nummots1[HH_dt_2_out$nummots == 0] <- HH_dt_2_out$nummots1[HH_dt_2_out$nummots == 0] + 0.0001

#HH_dt_2_out$parttime1 = HH_dt_2_out$parttime
#HH_dt_2_out$parttime1[HH_dt_2_out$parttime == 0] <- HH_dt_2_out$parttime1[HH_dt_2_out$parttime == 0] + 0.0001

#HH_dt_2_out$CSno <- 0
#HH_dt_2_out$CSno[HH_dt_2_out$CS == "no"] <- HH_dt_2_out$CSno[HH_dt_2_out$CS == "no"] + 1

#HH_dt_2_out$CSyes <- 0 
#HH_dt_2_out$CSyes[HH_dt_2_out$CS == "yes"] <- HH_dt_2_out$CSyes[HH_dt_2_out$CS == "yes"] + 1

#HH_dt_2_out$CSmultiple  <- 0
#HH_dt_2_out$CSmultiple[HH_dt_2_out$CS == "yes_multiple"] <- HH_dt_2_out$CSmultiple[HH_dt_2_out$CS == #"yes_multiple"] + 1

#as factors
#HH_dt_2_out$CSmultiple <- factor(HH_dt_2_out$CSmultiple)
#HH_dt_2_out$CSyes <- factor(HH_dt_2_out$CSyes)
#HH_dt_2_out$CSno <- factor(HH_dt_2_out$CSno)
```


```{r}
fit_multinom_null <- multinom(numcars ~ 1, data = HH_dt_2_out,maxit=350)

result_stepAIC2 <- stepAIC(fit_multinom_null, direction="forward", scope = list(upper = ~ numlic + I(numlic^2) + region2 + income_numerical + 
     I(income_numerical^2)+quali_nv + CSyes + workers + CSmultiple + log(nummots1) + housing_type + 
    triplength_avg + I(triplength_avg^2) + quali_opnv + oldHH + parttime +I(parttime^2) +tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28))

result_stepAIC2

model_nonlinear <- multinom(numcars ~ numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2)
, data = HH_dt_2_out,maxit=500)

# Mit mnlogit zum Vergleich

mnlogit_dt_out <- mlogit.data(HH_dt_2_out, choice = "numcars", shape = "wide") 

fm_new <- formula(numcars ~  1| numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2)|1)
fit_new <- mnlogit(fm_new, mnlogit_dt_out, ncores=4, choiceVar = "alt")


```

Test for influential points: standardized residuals

```{r}


unstandardizedResiduals <- residuals(model_nonlinear, outcome=FALSE)
 #get standardized values
standardizedResiduals <- (unstandardizedResiduals - mean(unstandardizedResiduals)) / sd(unstandardizedResiduals)

# no standardized residuals above 3 or below -3
SR_df <- as.data.frame(standardizedResiduals)
summary_SR <- summary(SR_df)
filter(SR_df, standardizedResiduals > 3 |standardizedResiduals <  -3)

#Table for Appendix:
summary_SR <- as.data.frame(summary_SR)
summary_SR <- separate(data = summary_SR, col = "Freq", into = c("Var", "Standardized Residuals"), sep = ":")
summary_SR$Var1 <- NULL
summary_SR$Var2 <- NULL

print(xtable(summary_SR, type = "latex",digits=c(0,0,3)),include.rownames=FALSE, file = "standardresid.tex")
```

