---
title: "Thesis_clean"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Nützliche Befehle
```{r}
#save.image(file='yoursession.RData')

#To load this data later you can use:

#load('yoursession.RData')
```

Packages and libraries

```{r}
#install.packages('mosaic')
#install.packages('interactions')
#install.packages('data.table')
#install.packages('magrittr')
#install.packages('tidyr')
#install.packages('dplyr')
#install.packages('interplot')
#install.packages("Hmisc")
#install.packages("corrplot")
#install.packages("PerformanceAnalytics")
#install.packages("mlogit", dependencies=TRUE)
#install.packages("foreign")
#install.packages("nnet")
#install.packages("ggplot2")
#install.packages("reshape2")
#install.packages("mnlogit")
#install.packages("Formula")
#install.packages("xtable")
#install.packages("psych")

library(margins)
library(psych)
library(xtable)
library(ggpubr)
library(reshape2)
library(interplot)
library(miscTools)
library(MASS)
library(car)
library(ggplot2)
library(mlogit)
library(nnet)
library(foreign)
library(data.table)
library(generalhoslem)
library(dplyr)
library(broom)
library(magrittr)
library(tidyr)
library(dplyr)
library(mnlogit)
library(Formula)
library(tibble)
library(mosaic)
library(Hmisc)
library(corrplot)
library(interactions)
library(PerformanceAnalytics)
library(Formula)
library(effects)
```

Import Data

```{r}

HH_file<- file.path('Data/MiD2017_Haushalte.csv')
HH_dt <- fread(HH_file)
HH_dt <- as.data.table(HH_dt)


Person_file <- file.path('Data/MiD2017_Personen.csv')
Person_dt <- fread(Person_file)
Person_dt <- as.data.table(Person_dt)

```


Check if the two files match
Yes, in the person file there are person for every household in the household file
```{r}
ids_HH <- HH_dt[, "H_ID"] # 156240
ids_P <- Person_dt[, "H_ID"]
unique_ids_P <- unique(ids_P) # 156240
count(unique_ids_P)
count(ids_HH)
```

How many households are there per number of cars
-> only 2% of households have four cars and more, therefore the grouping by only 0,1,2 and more than 3
cars is sufficient
```{r}
dplyr::count(HH_dt, anzauto_gr1)
3424/156420
# nur ca. 2 % der HH haben 4 Autos und mehr -> es reicht die Untergliederung bis 3 und mehr Autos zu verwenden 
```

Remove the 14 households that do not disclose their number of cars from the dataset
```{r}
dplyr::count(HH_dt, auto)
HH_dt <- filter(HH_dt, anzauto_gr2 != 9)
dplyr::count(HH_dt, H_ANZAUTO)
```

Remove columns there are not needed from the dataset

```{r}
HH_dt <- as.data.table(HH_dt)
HH_dt[, c("H_GEW","H_HOCH"):=NULL]

HH_dt <- HH_dt[, -c("H_NOCAR_B", "H_NOCAR_A", "H_NOCAR_C", "H_NOCAR_D", "H_NOCAR_E", "H_NOCAR_F","BLAND","pkw_status", "pkw_seg_kba", "pkw_jahresfl", "pkw_jahresfl_gr", "BLAND_GEO", "H_EINK", "hheink_gr1", "hhgr_oecd", "aq_eink", "oek_status")]
HH_dt[, c("MODE","BASISAUF", "TEILSTP", "H_NEBEN_1","H_NEBEN_2","H_NEBEN_3","H_NEBEN_4","H_NEBEN_5", "H_NEBEN_6", "H_NEBEN_7","H_NEBEN_8", "anzneben", "nebenws" ):=NULL]
HH_dt[, "hausnutz":=NULL]
HH_dt[, "wohnlage":=NULL]
HH_dt[, c("RegioStaR2","RegioStaR17"):=NULL]
HH_dt[, "H_MIETE":=NULL]
HH_dt[, "H_ART":=NULL]
HH_dt[, "mobtyp":= NULL]
HH_dt <- HH_dt[, -c("HP_SEX_1","HP_SEX_2","HP_SEX_3","HP_SEX_4","HP_SEX_5","HP_SEX_6","HP_SEX_7","HP_SEX_8")]
HH_dt[, c("anzauto_gr1","anzauto_gr3"):=NULL]
HH_dt[, "M_CAR":= NULL]
HH_dt[, "anzfs_gr":= NULL]
HH_dt[, "hhgr_gr":= NULL]
HH_dt[, "nocar":= NULL]
HH_dt[, "min_ozmz":= NULL]  
HH_dt[, "anzkind06":= NULL]
HH_dt[, "anzkind14":= NULL]
HH_dt[, "anzerw14":= NULL]
HH_dt[, "anzerw18":= NULL]
HH_dt[, "POLGK":= NULL]  
HH_dt[, "RegioStaRGem7":= NULL]  
HH_dt[, "RegioStaR4":= NULL]  
HH_dt[, "GEMTYP":= NULL]
HH_dt[, "SKTYP":= NULL]
```

Modelling explanatory variables 

1. Number of working people 

berufstätig:
1: Vollzeit berufstätig
2: Teilzeit berufstätig, d.h. 18 bis unter 35 Stunden pro Woche
3: geringfügig beschäftigt
4: berufstätig als Nebentätigkeit oder im Praktikum
5: berufstätig ohne Angabe zum Umfang
```{r}
taet_dt <- HH_dt[, c("HP_TAET_1","HP_TAET_2", "HP_TAET_3", "HP_TAET_4","HP_TAET_5","HP_TAET_6","HP_TAET_7","HP_TAET_8")]
summary(taet_dt)
taet_dt <- as.data.table(taet_dt)

temp_workersall <- taet_dt < 6 & taet_dt > 0
temp_workersall <- as.data.table(temp_workersall)
temp_workersall <- temp_workersall*1

temp_workers <- taet_dt == 1
temp_workers <- as.data.table(temp_workers)
temp_workers <- temp_workers*1

temp_parttime <- taet_dt < 6 & taet_dt > 1
temp_parttime <- as.data.table(temp_parttime)
temp_parttime <- temp_parttime*1

sum_workersall<- apply(temp_workersall,1,sum)
sum_workers<- apply(temp_workers,1,sum)
sum_parttime<- apply(temp_parttime,1,sum)
# add new column 
HH_dt$workersall <- sum_workersall
HH_dt$workers <- sum_workers
HH_dt$parttime <- sum_parttime

# remove old columns
HH_dt <- HH_dt[, -c("HP_TAET_1","HP_TAET_2", "HP_TAET_3", "HP_TAET_4","HP_TAET_5","HP_TAET_6","HP_TAET_7","HP_TAET_8")]

dplyr::count(HH_dt, workers)
dplyr::count(HH_dt, parttime)

```

2. Number of license holders

```{r}
# remove unlogical values and households that did not disclose number of holders
HH_dt <- filter(HH_dt, HP_ANZFS != 99 &HP_ANZFS != 94 )

dplyr::count(HH_dt, HP_ANZFS)
HH_dt <- as.data.table(HH_dt)


```

3. Household size 

```{r}
HH_dt <- as.data.table(HH_dt)
setnames(HH_dt, "H_GR", "hhsize")
dplyr::count(HH_dt, hhsize)

```

4. Age of household members

```{r}
# remove households that did not disclose age
HH_dt <- filter(HH_dt, HP_ALTER_1 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_2 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_3 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_4 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_5 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_6 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_7 != 999 )
HH_dt <- filter(HH_dt, HP_ALTER_8 != 999 )

age_dt <- HH_dt[, c("HP_ALTER_1", "HP_ALTER_2", "HP_ALTER_3", "HP_ALTER_4", "HP_ALTER_5", "HP_ALTER_6", "HP_ALTER_7", "HP_ALTER_8")]


summary(age_dt)
is.data.table(age_dt)

# 18-37 year olds
temp <- age_dt

result <- temp < 37 & temp > 17
result <- as.data.table(result)
result <- result*1
result
anzahl1836 <- apply(result,1,sum)

# 40-64 year olds

result3 <- temp < 65 & temp > 39
result3 <- as.data.table(result3)
result3 <- result3*1
anzahl4064 <- apply(result3,1,sum)


# 65 year olds and older

result2 <- temp > 64 & temp < 150
result2 <- as.data.table(result2)
result2 <- result2*1
anzahl65 <- apply(result2,1,sum)

result4 <- temp > 36 & temp < 150
result4 <- as.data.table(result4)
result4 <- result4*1
anzahlold <- apply(result4,1,sum)

# create new columns
HH_dt$num1836 <- anzahl1836
HH_dt$num4064 <- anzahl4064
HH_dt$num65 <- anzahl65
HH_dt$numold <- anzahlold


#remove old columns
HH_dt <- HH_dt[, -c("HP_ALTER_1", "HP_ALTER_2", "HP_ALTER_3", "HP_ALTER_4", "HP_ALTER_5", "HP_ALTER_6", "HP_ALTER_7", "HP_ALTER_8")]

# share noch hinzufügen?
```

5.
Household lifecycle stage 
-> single, couple, couple with children, singleparent and other (extended family, unattached individuals)

```{r}
# remove households that did not disclose hhtyp
HH_dt <- filter(HH_dt, hhtyp != 95)

hhtyp_dt <- HH_dt[, "hhtyp"]
hhtyp_dt <- as.data.table(hhtyp_dt)
hhtyp_dt[, "single"] <- 0
hhtyp_dt[, "couple"] <- 0
hhtyp_dt[, "couple_children"] <- 0
hhtyp_dt[, "singleparent"] <- 0
hhtyp_dt[, "otherindividuals"] <- 0


# Singles
temp2 <- hhtyp_dt[,1]

single <- temp2 < 4
single <- as.data.table(single)
single <- single*1

# Couples

couple <- temp2 < 7 & temp2 > 3
couple <- as.data.table(couple)
couple <- couple *1

# Couples with children

couple_c <- temp2 < 11 & temp2 > 7
couple_c <- as.data.table(couple_c)
couple_c <- couple_c*1

# singleparent

singleparent <- temp2 == 11
singleparent <- as.data.table(singleparent)
singleparent <- singleparent*1


# other individuals

others <- temp2 == 7
others <- as.data.table(others)
others <- others*1

#add new columns
HH_dt[, "single"] <- single
HH_dt[, "couple"] <- couple
HH_dt[, "couple_children"] <- couple_c
HH_dt[, "single_parent"] <- singleparent
HH_dt[, "other_ind"] <- others

#remove old columns
HH_dt <- as.data.table(HH_dt)
HH_dt[, "hhtyp":= NULL]
HH_dt[, "hhtyp2":= NULL]


#(relationshipstatus in one variable -> test difference)
temp_single <- HH_dt[, "single"]
temp_couple <- HH_dt[, "couple"]
temp_couplec <- HH_dt[, "couple_children"]
temp_singlep <- HH_dt[, "single_parent"]
temp_oth <- HH_dt[, "other_ind"]

temp_single <- temp_single*1
temp_couple <- temp_couple * 2
temp_couplec <- temp_couplec * 3
temp_singlep <- temp_singlep * 4
temp_oth <- temp_oth * 5

householdtype <- temp_single + temp_couple + temp_couplec + temp_singlep + temp_oth

#control:
dplyr::count(HH_dt, single)
dplyr::count(HH_dt, couple)
dplyr::count(HH_dt, single_parent)
dplyr::count(HH_dt, other_ind)
householdtype$single <- factor(householdtype$single)
summary(householdtype)
#assign new column
HH_dt$householdtype_all <- householdtype$single

```

6. Number of children
```{r}
# Spalte anzkind18

dplyr::count(HH_dt, anzkind18)


```

7. Motorräder und Fahrräder

```{r}
# H_ANZMOTMOP : anzahl an motorräder, mopeds, mofas im HH
# alle anderen entfernen:
HH_dt[, "auto":= NULL]
HH_dt[, "H_ANZMOT":= NULL]
HH_dt[, "H_ANZMOP":= NULL]
HH_dt[, "anzmotmop_gr":= NULL]
HH_dt[, "motmop":= NULL]

#anzpedrad: anzahl elektrofahrrad, pedelecs, fahrräder im HH
HH_dt[, "H_ANZPED":= NULL]
HH_dt[, "H_ANZRAD":= NULL]
HH_dt[, "anzped_gr":= NULL]
HH_dt[, "anzrad_gr":= NULL]
HH_dt[, "anzpedrad_gr":= NULL]
HH_dt[, "pedrad":= NULL]

#  remove households without information
HH_dt <- filter(HH_dt, H_ANZMOTMOP != 99)
HH_dt <- filter(HH_dt, anzpedrad != 99)

```

8. housing type and availability of a garage

```{r}
# haustyp: 1 ein-bis zweifamilienhaus, 2 mehrfamilienhaus, 3 geschosswohnungsbau, 4 sonstiges, 95 nicht zuzuordnen
dplyr::count(HH_dt, haustyp)
HH_dt <- filter(HH_dt, haustyp != 95)

#transform into factor
HH_dt$haustyp <- factor(HH_dt$haustyp)

# garage: 0 nein, 1 ja
dplyr::count(HH_dt, garage)
HH_dt <- filter(HH_dt, garage != 95)
setnames(HH_dt, "haustyp", "housing_type")

#transform into factor

HH_dt$garage<- factor(HH_dt$garage)
```


10. Variables regarding public transport and public services

```{r}
#bus28: airline distance (in groups) to the next busstop with at least 28 departures on workdays
#tram 28 ""
#bahn 28 ""

# change grouping for these variables to near, middle, far, very far and factorize them

# less than 500m: near
# less than 2.5km: middle
# less than 5km: far
# more than 5km: very far

dplyr::count(HH_dt, bus28)

temp_bus <- HH_dt[, "bus28"]
near <- temp_bus == 1 | temp_bus == 2
near <- near*1

middle <- temp_bus == 3 |temp_bus == 4
middle <- middle*2

far <- temp_bus == 5
far <- far * 3

rfar <- temp_bus == 6
rfar <- rfar * 4

bus <- near + middle + far + rfar 
#Kontrolle
dplyr::count(HH_dt, bus28)
bus <- factor(bus)
summary(bus)

# add column
HH_dt$bus28 <- bus
summary(HH_dt$bus28)

#same for train
dplyr::count(HH_dt, bahn28)
temp_train <- HH_dt[, "bahn28"]
near <- temp_train == 1 | temp_train == 2
near <- near*1

middle <- temp_train== 3 |temp_train == 4
middle <- middle*2

far <- temp_train == 5
far <- far * 3

rfar <- temp_train == 6
rfar <- rfar * 4

train<- near + middle + far + rfar 
#control
train <- factor(train)
summary(train)
dplyr::count(HH_dt, bahn28)

# add column
HH_dt$train28 <- train
summary(HH_dt$train28)
#remove old column
HH_dt[, "bahn28":= NULL]


#same for metro: (a lot of people for whom it is really far)
dplyr::count(HH_dt, tram28)
temp_tram <- HH_dt[, "tram28"]
near <- temp_tram == 1 | temp_tram == 2
near <- near*1

middle <- temp_tram == 3 |temp_tram == 4
middle <- middle*2

far <- temp_tram == 5
far <- far * 3

rfar <- temp_tram == 6
rfar <- rfar * 4

metro <- near + middle + far + rfar 
#Kontrolle
metro <- factor(metro)
summary(metro)
dplyr::count(HH_dt, tram28)

# add 
HH_dt$metro28 <- metro
#remove old column
HH_dt[, "tram28":= NULL]

#quali_opnv -> quality of public transport on a scale of 1 to 4

#quali_nv -> quality of public services (schools, supermarkets, doctors, pharmacys, etc.) on a scale of 1 to 4

dplyr::count(HH_dt, quali_opnv)
dplyr::count(HH_dt, quali_nv)

# remove households that did not disclose this information
HH_dt <- filter(HH_dt, quali_opnv!= 95)
HH_dt <- filter(HH_dt, quali_nv!= 95)


#transform into factors
#quali_nv
HH_dt$quali_nv<- factor(HH_dt$quali_nv)

#quali_opnv, ordered factor
HH_dt$quali_opnv<- factor(HH_dt$quali_opnv)

```

11. Regional type

```{r}
# variable RegioStaR7
# variable RegioStaRGem5
dplyr::count(HH_dt, RegioStaR7)
dplyr::count(HH_dt, RegioStaRGem5)
#oder RegiostarGem5:
#Metropole
#Regiopole, Großstadt
#zentrale Stadt, Mittelstadt 
#städtischer Raum
#kleinstädtischer, dörflicher Raum  
```

12. Carsharing

```{r}
#Abgebildet durch H_CS:
#1 ja, bei einem Anbieter
#2 ja, bei mehreren Anbietern 
#3 nein, gar nicht
#9 keine Angabe
dplyr::count(HH_dt, H_CS)

# remove households that did not disclose this information 
HH_dt <- filter(HH_dt, H_CS!= 9)
```

Merging data from the person data set

1. Highest type of education in the household

```{r}
education_dt <- Person_dt[, c("H_ID", "P_BIL")]
Anzahl_HH <- unique(bildung_dt[, "H_ID"])
count(Anzahl_HH)
education_withoutProxy <- education_dt[P_BIL != "206" & P_BIL!= "9" & P_BIL!= "6"]
Anzahl_HH_withoutproxy <- unique(education_withoutProxy[, "H_ID"])
count(Anzahl_HH_withoutproxy)

# find highest degree per household
maxEducation_byHH <- max(P_BIL ~ H_ID, data = education_withoutProxy)
maxEducation_dt <- as.data.table(data.frame(HH_ID=names(maxEducation_byHH), maxEducation=maxEducation_byHH, row.names=NULL))
summary(maxEducation_dt)

dplyr::count(maxEducation_dt, maxEducation)

``` 
2. Number of trips on a given day per household

```{r}

trips_dt <- Person_dt[, c("H_ID", "anzwege2", "arbwo", "feiertag")]

#remove person with unknown number of trips
trips_dt <- trips_dt[anzwege2 != "803" & anzwege2!= "804"]

#remove persons that were measured on weekends or holidays
trips_workdays <- trips_dt[arbwo == 1 & feiertag == 0]

x <- sum(anzwege2 ~ H_ID, data = trips_workdays)
numberoftrips_dt <- as.data.table(data.frame(HH_ID=names(x), trips=x, row.names=NULL))
dplyr::count(numberoftrips_dt, trips)
summary(numberoftrips_dt)


```

3. Länge der Wege am Stichtag

```{r}
#perskm2 enthält länge aller wege mit weiteren wegen ohne rbw, fehlende werte wurden imputiert
triplength_dt <- Person_dt[, c("H_ID", "perskm2", "arbwo", "feiertag")] 
triplength_dt <- triplength_dt[arbwo == 1 & feiertag == 0]

summary(triplength_dt)

#remove households without information on trips
triplength_clean <- triplength_dt[perskm2 != "80803" & perskm2!= "80804" & perskm2 != "80802"]

# perskm2 is a character column, we need to convert it to numeric to be able to sum it up
triplength_clean$perskm2 <- sub("," , ".", triplength_clean$perskm2)
triplength_clean$perskm2 <- as.numeric(triplength_clean$perskm2)


dplyr::count(triplength_clean, perskm2)

x <- sum(perskm2 ~ H_ID, data = triplength_clean)
totaltriplength_dt <- as.data.table(data.frame(HH_ID=names(x), perskm2=x, row.names=NULL))

summary(totaltriplength_dt)
dplyr::count(totaltriplength_dt, perskm2)

```  

Merge all three features

```{r}
#1. maxEducation_dt 

#2. numberoftrips_dt

combined2_df <- merge(x=maxEducation_dt,y=numberoftrips_dt,by="HH_ID")

#3. gesamteWeglänge_dt

combined3_df <- merge(x=combined2_df, y=totaltriplength_dt, by="HH_ID")

```

Combine both data tables

```{r}
HH_dt <- as.data.table(HH_dt)
setnames(HH_dt, "H_ID", "HH_ID")
HH_dt$HH_ID <- factor(HH_dt$HH_ID)

HH_dt_2 <- merge(x=combined3_df, y=HH_dt, by="HH_ID")

```

Add a column for adverage triplength
```{r}

HH_dt_2$triplength_avg <- HH_dt_2$perskm2/HH_dt_2$trips

#Nan durch 0 ersetzen 
HH_dt_2[is.na(HH_dt_2)] <- 0

summary(HH_dt_2$triplength_avg)

#log transformation?
#HH_dt_final$Weglänge_avg <- log(HH_dt_final$Weglänge_avg)
# transform -inf to zero 
#HH_dt_final[HH_dt_final == -Inf] <- 0

summary(HH_dt_2$trips)
setnames(HH_dt_2, "perskm2", "triplength")

```


9. Income

```{r}
# income as a number, with imputed values : hheink_imp
#outlier removal
dplyr::count(HH_dt_2, hheink_imp)
summary(HH_dt_2$hheink_imp)
HH_dt_2$hheink_imp <- sub("," , ".", HH_dt_2$hheink_imp)
HH_dt_2$hheink_imp <- as.numeric(HH_dt_2$hheink_imp)
summary(HH_dt_2$hheink_imp)

setnames(HH_dt_2, "hheink_imp", "income_numerical")

# change scale of income
HH_dt_2$income_numerical <- HH_dt_2$income_numerical/1000

#income in groups

dplyr::count(HH_dt, hheink_gr2)
# bis 2000: 1 
# zwischen 2000 - 4000 2
# 4000 - 7000 3
# more than 7000 4

temp_income <- HH_dt_2[, "hheink_gr2"]

low <- temp_income == 1 | temp_income == 2| temp_income == 3 | temp_income == 4
low <- low*1

middle <- temp_income == 5 |temp_income == 6
middle <- middle*2

high <- temp_income == 7 | temp_income == 8 | temp_income == 9 
high <- high * 3

highest <- temp_income == 10 
highest <- highest * 4

income <- low + middle + high + highest 
# control:
dplyr::count(HH_dt_2, hheink_gr2)
income <- factor(income)
summary(income)

# add new column 
HH_dt_2$income_gr <- income

# delete old income column 
HH_dt_2<- as.data.table(HH_dt_2)
HH_dt_2[, hheink_gr2:= NULL]

```

Further datawrangling

Making actual datatable by reducing some categories, factorizing etc. 

```{r}
#change name of dependent variable
setnames(HH_dt_2, "anzauto_gr2", "anzauto")

# education as factor, not ordinal
HH_dt_2$maxEducation<- factor(HH_dt_2$maxEducation)
summary(HH_dt_2$maxEducation)
# change Name
setnames(HH_dt_2, "maxEducation", "education")

# change name motor vehicles and bikes
setnames(HH_dt_2, "H_ANZMOTMOP", "nummots")
setnames(HH_dt_2, "anzpedrad", "numped")

#change name for number of licenses
dplyr::count(HH_dt_2, HP_ANZFS)
setnames(HH_dt_2, "HP_ANZFS", "numlic")

#change name for H_CS and make into factor
setnames(HH_dt_2, "H_CS", "CS")
HH_dt_2$CS<- factor(HH_dt_2$CS)

# change name for region variables and change into factors
# RegioStarGem5
setnames(HH_dt_2, "RegioStaRGem5", "region1")
dplyr::count(HH_dt_2, region1)
HH_dt_2$region1 <- factor(HH_dt_2$region1)

# RegiostaR7
setnames(HH_dt_2, "RegioStaR7", "region2")

#group according to:
#Urban (71+72)
#Mid-urban (73, 75, 76)
#Rural (74, 77)

dplyr::count(HH_dt_2, region2)

temp_region2 <- HH_dt_2[, "region2"]
urban <- temp_region2 == 71 | temp_region2 == 72
urban <- urban*1

midurban <- temp_region2 == 73 | temp_region2 == 75 | temp_region2 == 76
midurban <- midurban*2

rural <- temp_region2 == 74 | temp_region2 == 77
rural <- rural * 3

region2 <- urban + midurban + rural 
#control
dplyr::count(HH_dt_2, region2)
region2 <- factor(region2)
summary(region2)

# add column:
HH_dt_2$region2 <- region2
summary(HH_dt_2$region2)

setnames(HH_dt_2, "anzauto", "numcars")
setnames(HH_dt_2, "anzkind18", "numch18")

HH_dt_2$single <- factor(HH_dt_2$single)
HH_dt_2$couple <- factor(HH_dt_2$couple)
HH_dt_2$couple_children <- factor(HH_dt_2$couple_children)
HH_dt_2$single_parent <- factor(HH_dt_2$single_parent)
HH_dt_2$other_ind <- factor(HH_dt_2$other_ind)
HH_dt_2$numcars <- factor(HH_dt_2$numcars)


```


Rename factor levels 

```{r}
library(plyr)
library(dplyr)
HH_dt_2$income_gr = revalue(HH_dt_2$income_gr, c("1"="low", "2"="middle", "3"="high", "4" = "veryhigh"))
HH_dt_2$householdtype_all= revalue(HH_dt_2$householdtype_all, c("1"="single", "2"="couple", "3"="couple_children", "4" = "single_parent", "5"="other_ind"))
HH_dt_2$housing_type = revalue(HH_dt_2$housing_type, c("1"="singlefamily_h", "2"="multifamily_h", "3"="apartmentbuilding", "4" = "other"))
HH_dt_2$education = revalue(HH_dt_2$education, c("1"="none", "2"="Hauptschule", "3"="Realschule", "4" = "Abitur", "5"="university"))
HH_dt_2$region2 = revalue(HH_dt_2$region2, c("1"="urban", "2"="suburban", "3"="rural"))
HH_dt_2$CS = revalue(HH_dt_2$CS, c("1"="yes", "2"="yes_multiple", "3"="no"))
HH_dt_2$bus28 = revalue(HH_dt_2$bus28, c("1"="near", "2"="middle", "3"="far", "4" = "rfar"))
HH_dt_2$train28 = revalue(HH_dt_2$train28, c("1"="near", "2"="middle", "3"="far", "4" = "rfar"))
HH_dt_2$metro28 = revalue(HH_dt_2$metro28, c("1"="near", "2"="middle", "3"="far", "4" = "rfar"))

HH_dt_2$region1 = revalue(HH_dt_2$region1, c("51"="metropole", "52"="regiopole", "53"="city", "54" = "urbanarea", "55"="ruralarea"))

```
Add share columns

```{r}
HH_dt_2$share1836 <- HH_dt_2$num1836/HH_dt_2$hhsize
HH_dt_2$share4064 <- HH_dt_2$num4064/HH_dt_2$hhsize

HH_dt_2$shareold <- HH_dt_2$numold/(HH_dt_2$hhsize-HH_dt_2$numch18)
HH_dt_2$shareyoung <- HH_dt_2$num1836/(HH_dt_2$hhsize-HH_dt_2$numch18)

HH_dt_2$shareworkers <- HH_dt_2$workers/HH_dt_2$hhsize
HH_dt_2$shareparttime <- HH_dt_2$parttime/HH_dt_2$hhsize
HH_dt_2$tripsavg <- HH_dt_2$trips/HH_dt_2$hhsize

HH_dt_2$youngHH <- 0
HH_dt_2$youngHH[HH_dt_2$shareyoung > 0.5] <- 1
HH_dt_2$youngHH <- factor(HH_dt_2$youngHH)

HH_dt_2$oldHH <- 0
HH_dt_2$oldHH[HH_dt_2$shareyoung <= 0.5] <- 1
HH_dt_2$oldHH <- factor(HH_dt_2$oldHH)


```

Add "households with children" column 

```{r}
HH_dt_2$couple_children <- as.numeric(as.character(HH_dt_2$couple_children))
HH_dt_2$single_parent <- as.numeric(as.character(HH_dt_2$single_parent))
HH_dt_2$hh_children<- HH_dt_2$couple_children + HH_dt_2$single_parent
HH_dt_2$hh_children <- as.factor(HH_dt_2$hh_children)
HH_dt_2$couple_children <- factor(HH_dt_2$couple_children)
HH_dt_2$single_parent <- factor(HH_dt_2$single_parent)


```

Make separate columns out of CS column 
```{r}
HH_dt_2$CSno <- 0
HH_dt_2$CSno[HH_dt_2$CS == "no"] <- HH_dt_2$CSno[HH_dt_2$CS == "no"] + 1

HH_dt_2$CSyes <- 0 
HH_dt_2$CSyes[HH_dt_2$CS == "yes"] <- HH_dt_2$CSyes[HH_dt_2$CS == "yes"] + 1

HH_dt_2$CSmultiple  <- 0
HH_dt_2$CSmultiple[HH_dt_2$CS == "yes_multiple"] <- HH_dt_2$CSmultiple[HH_dt_2$CS == "yes_multiple"] + 1

#as factors
HH_dt_2$CSmultiple <- factor(HH_dt_2$CSmultiple)
HH_dt_2$CSyes <- factor(HH_dt_2$CSyes)
HH_dt_2$CSno <- factor(HH_dt_2$CSno)


#make separate columns out of quali_nv:
HH_dt_2$qualinv1 <- 0
HH_dt_2$qualinv1[HH_dt_2$quali_nv == "1"] <- HH_dt_2$qualinv1[HH_dt_2$quali_nv == "1"] + 1

HH_dt_2$qualinv2 <- 0
HH_dt_2$qualinv2[HH_dt_2$quali_nv == "2"] <- HH_dt_2$qualinv2[HH_dt_2$quali_nv == "2"] + 1

HH_dt_2$qualinv3  <- 0
HH_dt_2$qualinv3[HH_dt_2$quali_nv == "3"] <- HH_dt_2$qualinv3[HH_dt_2$quali_nv == "3"] + 1

HH_dt_2$qualinv4  <- 0
HH_dt_2$qualinv4[HH_dt_2$quali_nv == "4"] <- HH_dt_2$qualinv4[HH_dt_2$quali_nv == "4"] + 1

HH_dt_2$qualinv1 <- factor(HH_dt_2$qualinv1)
HH_dt_2$qualinv2 <- factor(HH_dt_2$qualinv2)
HH_dt_2$qualinv3 <- factor(HH_dt_2$qualinv3)
HH_dt_2$qualinv4 <- factor(HH_dt_2$qualinv4)



```

